---
title: '1'
author: "Yuka Chen"
date: "11/29/2021"
output: html_document
---
with(pre_survey, table(Y, X))
with(pre_survey, do.call(rbind, tapply(year_born, Foreign_born_or_Not, function(x) c(M = mean(x), SD = sd(x)))))

factor_temperature_vector <- factor(temperature_vector, order = TRUE, 
                                    levels = c("Low", "Medium", "High"))

```{r}
library(readr)
pre_survey <- read_csv("~/Desktop/GOVT650/ResearchProject/Data/oragnized data/pre_survey.csv", 
    na = "NA")

summary(pre_survey)

with(pre_survey, table(Gender, Likely_vote))



```


```{r}
library(tidyverse)
pre_survey %>% 
  filter(Citizen_or_not == "(1) Citizen") %>% 
  drop_na(Registered_or_not)-> mydata

with(mydata, table(Registered_or_not, Foreign_born_or_Not)) -> p
plot(p,main="Type of Citizens Whether they Register to vote",
        xlab="Registered or Not Registered",
        ylab="Type of Citizens")

library(stats)
t.test(mydata$Registered_or_not)

chisq.test(mydata$Registered_or_not,mydata$Foreign_born_or_Not,simulate.p.value = TRUE)

fisher.test(mydata$Registered_or_not, mydata$Foreign_born_or_Not) ## p-value 0.0000005095
p
```
We have a chi-squared value of 23.762. Since we get a p-Value less than the significance level of 0.05, we reject the null hypothesis and conclude that the two variables are in fact dependent.

```{r}
library(gtsummary)
tbl_cross(pre_survey, row=Foreign_born_or_Not, col=Registered_or_not, percent="row")
```

