---
title: "analysis"
author: "Yuka Chen"
date: "11/23/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
library(ggThemeAssist)
library(esquisse)
library(formattable)
require(foreign)
require(ggplot2)
require(MASS)
require(Hmisc)
require(reshape2)
```

```{r}
##load data 
library(readr)
presurvey <- read_csv("~/Desktop/GOVT650/ResearchProject/Data/oragnized data/presurvey.csv")
```


```{r}

pre_survey %>% 
  filter(Citizen_or_not == "(1) Citizen", Foreign_born_or_Not =="(0) Native") %>% ## filter to find 
  count(Registered_or_not)

total <- sum(808+99+5+2)

n_percent_registered <- (808 / total) * 100
n_percent_notregister <- (99 / total) * 100
n_percent_notesure <- (5 / total) * 100
n_percent_notelegible <- (2 / total) * 100

n_percent_registered
n_percent_notregister
n_percent_notesure 
n_percent_notelegible


pre_survey %>% 
  filter(Citizen_or_not == "(1) Citizen", Foreign_born_or_Not =="(1) Foreign") %>% 
  count(Registered_or_not)

total1 <- sum(1665+378+26+2)
f_percent_registered <- (1665 / total1) * 100
f_percent_notregister <- (378 / total1) * 100
f_percent_notesure <- (26 / total1) * 100
f_percent_notelegible <- (2 / total1) * 100
f_percent_registered
f_percent_notregister
f_percent_notesure 
f_percent_notelegible

##the graph shows the porportion of native born american citizens and naturalized citizens. 
##It seems that naturalized citizens plan to votes mores as (4) not sure, havent thought about it is less

pre_survey %>% 
  filter(Registered_or_not == "(1) Yes, Registered", Citizen_or_not == "(1) Citizen") %>%
  count(Foreign_born_or_Not) -> y

pre_survey %>% 
  filter(Registered_or_not == "(2) Not Registered",Citizen_or_not == "(1) Citizen") %>%
  count(Foreign_born_or_Not) -> n

pre_survey %>% 
  filter(Registered_or_not == "(3) DO NOT READ  Not Sure Currently Registered",Citizen_or_not == "(1) Citizen") %>%
  count(Foreign_born_or_Not) -> n

Registered_vote_citizens <- matrix(c(808, 1665,99,378),nrow = 2, ncol = 2, byrow = TRUE)
rownames(Registered_vote_citizens) <- c("Native Born Citizen","Naturalized Citizen")
colnames(Registered_vote_citizens) <- c("Registered to Vote","Not register to Vote")

chisq.test(Registered_vote_citizens)

yes_registered <- 808*1665
no_registered <- 99*378
yes_register1 <- 808/yes_registered
no_registered1 <- 99/no_registered
proportions_difference <- yes_register1 - no_registered1
proportions_difference

odds_ratio <- (808*378)/(99*1665)
odds_ratio

chi_test_registered <- matrix(c(808,1665,99,378))
```

\newpage

#2.	the longer the Naturalized American stay in US, the more likely plan to vote
a.	Independent: Naturalized American’s year of arriving US 
b.	Dependent: Opinions/Plan to vote.
c.	S9, Q1.1, Q8_18, Q1.2, Q1.4 

```{r}
pre_survey %>% 
  filter(Citizen_or_not == "(1) Citizen",Foreign_born_or_Not == "(1) Foreign", Registered_or_not == "(1) Yes, Registered") %>% 
  mutate(Registered_or_not = recode(Registered_or_not,
                                      `(2) Not Registered`  = "Not Registered",
                                      `(1) Yes, Registered` = "Yes, Registered",
                                      `(3) DO NOT READ  Not Sure Currently Registered` = "Not Sure Currently Registered",
                                      `(4) DO NOT READ  Not eligible to vote/register` = "Not eligible to vote/register")) %>% 
  drop_na(Registered_or_not)-> naturalized_vote ## registered naturalized citizens

naturalized_vote %>% 
  ggplot(aes(x = Year_In_US,
           fill = Registered_or_not)) + 
  geom_bar()+
  labs(x = "Year Arrived in U.S.", y = "Numbers of Natualized Citizen Plan to Vote",
    fill = "Registered")

pre_survey %>% 
  ggplot(aes(x = Year_In_US,
           y = Registered_or_not)) + 
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

naturalized_vote %>% 
  drop_na(Likely_vote) %>% 
  ggplot(aes(x = Year_In_US, fill =Likely_vote))+
  geom_bar()+
  theme_minimal()+
    labs(x = "Year Arrived in U.S.", y = "Numbers of Natualized Citizen",
    fill = "Likely to Vote")
#########)+
  labs(x = "Year arrived in US", fill = "Likely Vote")

summary(naturalized_vote$Year_In_US)

#########
```


```{r}
library(ggplot2)
library(ggridges)


naturalized_vote %>% 
   filter(Citizen_or_not == "(1) Citizen",Foreign_born_or_Not == "(1) Foreign") %>% 
  mutate(Likely_vote = recode(Likely_vote,
                             `(1) I am absolutely certain I will vote` = "I am absolutely certain I will vote",     
                             `(2) I am pretty likely to vote` = "I am pretty likely to vote",
                             `(5) I will not vote this year` = "I will not vote this year",
                             `(4) My chances of voting are less than 50-50` = "My chances of voting are less than 50-50",
                             `(3) My chances of voting are 50-50` = "3")) -> fact_vote1
pre_survey %>% 
ggplot(aes(x = Year_In_US, y = Likely_vote,fill = Citizen_or_not)) +
  geom_density_ridges() + 
  theme_ridges() +
  theme(legend.position = "none")


library(ggbeeswarm)
library(scales)
fact_vote1 %>% 
ggplot(aes( x = factor(Likely_vote,
                      labels = c( "I am absolutely certain I will vote", "I am pretty likely to vote", "My chances of voting are 50-50", "My chances of voting are less than 50-50","I will not vote this year")), 
            y = Year_In_US,
           color = Likely_vote)) +
  geom_quasirandom(alpha = 0.7,
                   size = 1.5)+
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position = "none")

pre_survey %>% 
ggplot(aes(x = Year_In_US, y = Likely_vote, color = Foreign_born_or_Not)) +
  geom_jitter(alpha = 0.7,
              size = 1.5)+
  theme_minimal() +
  theme(legend.position = "none")


lapply(fact_vote1, FUN=summary)
```


```{r}
####### Before 1985
##"I am absolutely certain I will vote" percentage : 36.45%
fact_vote_analysis1 <- fact_vote1 %>% 
  filter(Likely_vote == "I am absolutely certain I will vote", Year_In_US < 1985)
fact_vote_analysis11 <- (nrow(fact_vote_analysis1)/nrow(fact_vote1))*100
fact_vote_analysis11
##"I am pretty likely to vote" percentage: 3.12%
fact_vote_analysis2 <- fact_vote1 %>% 
  filter(Likely_vote == "I am pretty likely to vote", Year_In_US < 1985)
fact_vote_analysis22 <- (nrow(fact_vote_analysis2)/nrow(fact_vote1))*100
fact_vote_analysis22
##"My chances of voting are 50-50" percentage: 0%
fact_vote_analysis3 <- fact_vote1 %>% 
  filter(Likely_vote == "My chances of voting are 50-50", Year_In_US < 1985)
fact_vote_analysis33 <- (nrow(fact_vote_analysis3)/nrow(fact_vote1))*100
fact_vote_analysis33
##"My chances of voting are less than 50-50": 1.14%
fact_vote_analysis4 <- fact_vote1 %>% 
  filter(Likely_vote == "My chances of voting are less than 50-50", Year_In_US < 1985)
fact_vote_analysis44 <- (nrow(fact_vote_analysis4)/nrow(fact_vote1))*100
fact_vote_analysis44
##"I will not vote this year": 1.26% 
fact_vote_analysis5 <- fact_vote1 %>% 
  filter(Likely_vote == "I will not vote this year", Year_In_US < 1985)
fact_vote_analysis55 <- (nrow(fact_vote_analysis5)/nrow(fact_vote1))*100
fact_vote_analysis55
```


```{r}
########## after 1985

##"I am absolutely certain I will vote" percentage : 33.33%
fact_vote_analysis111 <- fact_vote1 %>% 
  filter(Likely_vote == "I am absolutely certain I will vote", Year_In_US > 1985)
fact_vote_analysis1111 <- (nrow(fact_vote_analysis111)/nrow(fact_vote1))*100
fact_vote_analysis1111
##"I am pretty likely to vote" percentage: 4.86%
fact_vote_analysis222 <- fact_vote1 %>% 
  filter(Likely_vote == "I am pretty likely to vote", Year_In_US > 1985)
fact_vote_analysis2222 <- (nrow(fact_vote_analysis222)/nrow(fact_vote1))*100
fact_vote_analysis2222
##"My chances of voting are 50-50" percentage: 0%
fact_vote_analysis333 <- fact_vote1 %>% 
  filter(Likely_vote == "My chances of voting are 50-50", Year_In_US > 1985)
fact_vote_analysis3333 <- (nrow(fact_vote_analysis33)/nrow(fact_vote1))*100
fact_vote_analysis3333
##"My chances of voting are less than 50-50": 1.38%
fact_vote_analysis444 <- fact_vote1 %>% 
  filter(Likely_vote == "My chances of voting are less than 50-50", Year_In_US > 1985)
fact_vote_analysis4444 <- (nrow(fact_vote_analysis444)/nrow(fact_vote1))*100
fact_vote_analysis4444
##"I will not vote this year": 1.14%
fact_vote_analysis555 <- fact_vote1 %>% 
  filter(Likely_vote == "I will not vote this year", Year_In_US > 1985)
fact_vote_analysis5555 <- (nrow(fact_vote_analysis555)/nrow(fact_vote1))*100
fact_vote_analysis5555
```


```{r}
#Exploratory data analysis </span>
#Summarizing the data
naturalized_vote %>% 
  dplyr::select(Likely_vote, Registered_or_not, Foreign_born_or_Not) -> naturalized_vote2
summary(naturalized_vote2)

naturalized_vote2
library("nnet")
test <- multinom(Likely_vote ~ Year_In_US, data = pre_survey)
summary(test)

###########
fact_vote1 %>% 
  factor(Likely_vote,
                      labels = c( "I am absolutely certain I will vote", "I am pretty likely to vote", "My chances of voting are 50-50", "My chances of voting are less than 50-50","I will not vote this year"))

model_sex <- lm(Likely_vote ~ Year_In_US, data = pre_survey)
summary(model_sex)$coef


naturalized_vote %>% 
   filter(Citizen_or_not == "(1) Citizen",Foreign_born_or_Not == "(1) Foreign") %>% 
  mutate(Likely_vote_dummy = recode(Likely_vote,
                             `(1) I am absolutely certain I will vote` = "1",     
                             `(2) I am pretty likely to vote` = "2",
                             `(5) I will not vote this year` = "3",
                             `(4) My chances of voting are less than 50-50` = "4",
                             `(3) My chances of voting are 50-50` = "3")) -> naturalized_likely_vote_dummy

##turn every variables into factors
naturalized_likely_vote_dummy %>% 
  mutate(across(where(is.factor), as.character)) -> naturalized_likely_vote_dummy2
model_likely <- lm(Likely_vote_dummy ~ Year_In_US, data = naturalized_likely_vote_dummy2)
summary(model_likely)$coef

##change all variables into numerical
naturalized_likely_vote_dummy %>% 
mutate(across(where(is.numeric), function(x) tidyr::replace_na(x, 0))) ->naturalized_likely_vote_dummy3
cor(naturalized_likely_vote_dummy3[,c("Likely_vote_dummy", "Year_In_US")])
model_likely <- lm(Likely_vote_dummy ~ Year_In_US, data = naturalized_likely_vote_dummy2)
summary(model_likely)$coef

model_likely_anova <- aov(Likely_vote_dummy ~ Year_In_US, data = naturalized_likely_vote_dummy2)

summary(model_likely_anova)
t.test(Likely_vote_dummy ~ Year_In_US, data = naturalized_likely_vote_dummy2)
```


```{r}
## the average of year of arrival of naturalized citizens who planned to vote is 1985. 
##The earliest was 1918. The year of arrival has the most people is 1980.




naturalized_vote %>% 
  mutate(Likely_vote = recode(Likely_vote,
                             `(1) I am absolutely certain I will vote` = "1",     
                             `(2) I am pretty likely to vote` = "2",
                             `(5) I will not vote this year` = "5",
                             `(4) My chances of voting are less than 50-50` = "4",
                             `(3) My chances of voting are 50-50` = "3")) -> fact_vote



fact_vote$Likely_vote.f = factor(fact_vote$Likely_vote,
                            ordered = TRUE,
                            levels = c("1", "2", "3", "4", "5"))

lm_likely <- lm(fact_vote$Likely_vote ~ Year_In_US, data = fact_vote$Likely_vote.f)
summary(lm_likely)

unique(naturalized_vote$Likely_vote)

```



```{r}
Mode <- function(x) {
    ux <- unique(x)
    ux[which.max(tabulate(match(x, ux)))]
}

Mode(naturalized_vote$Year_In_US)

## Because the mean is 1985 and the mode is 1980, I decided to add 5 years more to 1985 and reduce 5 years to 1975 to find out if people arrived earlier would tend to vote more comparing to those who arrive in the recent year


pre_survey %>% 
  filter(Citizen_or_not == "(1) Citizen",Foreign_born_or_Not == "(1) Foreign") %>% 
  mutate(Registered_or_not = recode(Registered_or_not,
                                      `(2) Not Registered`  = "Not Registered",
                                      `(1) Yes, Registered` = "Yes, Registered",
                                      `(3) DO NOT READ  Not Sure Currently Registered` = "Not Sure Currently Registered",
                                      `(4) DO NOT READ  Not eligible to vote/register` = "Not eligible to vote/register")) %>% 
  drop_na(Registered_or_not) -> naturalized_year
naturalized_year %>% 
  filter(Year_In_US > 1985 | Year_In_US < 1985) %>% 
  mutate(Arrival = ifelse(Year_In_US > 1985, "After 1985", "Before 1985")) %>% 
  ggplot(aes(x = Arrival, fill = Registered_or_not)) +
  geom_bar(position = "fill")

naturalized_year %>% 
  filter(Year_In_US > 1985 | Year_In_US < 1985) %>% 
  mutate(Arrival = ifelse(Year_In_US > 1985, "After 1985", "Before 1985")) %>% 
  ggplot(aes(x = Arrival, fill = Likely_vote)) +
  geom_bar(position = "fill")


##from the graphs we can see that porportion of people who registered voting are mostly arrived before 1975.


```




\newpage
#3.	immigrant who plan to vote are the people who talk politics.
a.	Independent: Immigration status + absolutely plan to vote
b.	Dependent: Yes/No on discussing politics with family and friends
c.	Q1.4 (status), Q1.4, Q5.1.1



```{r}
pre_survey %>% 
  filter(Citizen_or_not == "(1) Citizen",Foreign_born_or_Not == "(1) Foreign", Registered_or_not == "(1) Yes, Registered" | Likely_vote == "(1) I am absolutely certain I will vote") %>% 
  mutate(Registered_or_not = recode(Registered_or_not,
                                      `(2) Not Registered`  = "Not Registered",
                                      `(1) Yes, Registered` = "Yes, Registered",
                                      `(3) DO NOT READ  Not Sure Currently Registered` = "Not Sure Currently Registered",
                                      `(4) DO NOT READ  Not eligible to vote/register` = "Not eligible to vote/register"),
        Foreign_born_or_Not = recode(Foreign_born_or_Not,
                                     `(1) Foreign` = "Naturalized Citizen Who Planned on Voting")) %>% drop_na(Registered_or_not) -> vote_immigrant_talk

vote_immigrant_talk %>% 
  mutate(Often_discuss_poltics = recode(Often_discuss_poltics,
                                      `(3) Somewhat often` = "Somewhat often",
                                      `(1) Not at all`  = "Not at all",   
                                      `(2) Not too often` = "Not too often",
                                      `(4) Very often` = "Very often")) %>% 
  drop_na(Often_discuss_poltics) %>% 
  ggplot(aes(x = Foreign_born_or_Not, fill = Often_discuss_poltics))+
  geom_bar(position = "dodge")+
  labs(x = "Immigrants Who Planned on Voting",
    y = "Numbers of Voting Decisions", fill = "Frequency on Political Discussion w/ Family")

vote_immigrant_talk %>% 
    mutate(Interested_In_Politics = recode(Interested_In_Politics,
                                      `(1) Not at all interested` = "Not at all interested",
                                      `(2) Somewhat interested`  = "Somewhat interested",   
                                      `(3) Interested` = "Interested",
                                      `(4) Very interested` = "Very interested")) %>% 
  drop_na(Interested_In_Politics) %>% 
  ggplot(aes(x = Foreign_born_or_Not, fill = Interested_In_Politics))+
  geom_bar(position = "dodge")+labs(x = "Immigrants Who Planned on Voting",
    y = "Numbers of Voting Decisions", fill = "Interests in Politics") -> v3
v3

pie <- v3 + coord_polar("y", start=0)
pie

## From the graphs, we found the immigrants that plan on voting do not discuss politics with their family often, however, majority of them are somewhat interested in politics
```


```{r}

vote_immigrant_talk %>% 
  count(Interested_In_Politics)


total <- length(vote_immigrant_talk$Foreign_born_or_Not)


percent_Not_at_all_interested <- (242 / total) * 100
percent_Somewhat_interested <- (570 / total) * 100
percent_Interested <- (504 / total) * 100
percent_Very_interested <- (393 / total) * 100

percent_Not_at_all_interested 
percent_Somewhat_interested
percent_Interested
percent_Very_interested



##Not at all interested: 14% 
##Somewhat_interested: 33%
##Interested: 29%
##Very_interested: 22.86
```

\newpage
#4.	American who were born in US talk more politics than foreign born American/Naturalized American. 
a.	Independent: Type of American
b.	Dependent: interested in politics or not
c.	S9, Q1.4 (status), Q5.1.1

\newpage
#5.	American who identified as Asian American talk less politics and are the least ethnic group plan on voting.
a.	Independent: ethnicity 
b.	Dependent: interested in politics or not
c.	S10, S10_601, Q1.4 (status), Q5.1.1

```{r}
pre_survey %>% 
  filter(Citizen_or_not == "(1) Citizen") %>% 
  mutate(Foreign_born_or_Not = recode(Foreign_born_or_Not,
                                     `(0) Native` = "America Born Citizen",
                                     `(1) Foreign`= "Naturalized Citizen"),
         Often_discuss_poltics = recode(Often_discuss_poltics,
                                      `(3) Somewhat often` = "Somewhat often",
                                      `(1) Not at all`  = "Not at all",   
                                      `(2) Not too often` = "Not too often",
                                      `(4) Very often` = "Very often"))%>% 
  drop_na(Often_discuss_poltics) -> a
a %>% 
  ggplot(aes(x = Foreign_born_or_Not,
           fill = Often_discuss_poltics)) + 
  geom_bar(position = "fill")
```
```{r}
pre_survey %>% 
  filter(Citizen_or_not == "(1) Citizen") %>% 
  mutate(Foreign_born_or_Not = recode(Foreign_born_or_Not,
                                     `(0) Native` = 0,
                                     `(1) Foreign`= 1),
         Often_discuss_poltics = recode(Often_discuss_poltics,
                                      `(3) Somewhat often` = 1,
                                      `(1) Not at all`  = 0,   
                                      `(2) Not too often` = 0,
                                      `(4) Very often` = 1)) 
```

